Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-11-11 summary.Rmd
minor update

For modularity maximization, \citet{307cbeb9b1be48299388437423d94bf1} used the 
Extreme Points (EP) algorithm \cite{le2016}, which is specific to the case 
$K = 2$. In our simulation studies, we used the EP algorithm for $K = 2$ and 
the Louvain algorithm for $K > 2$. The Louvain algorithm is described by the 
following:

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Modularity maximization (Louvain Method)}
  \KwData{Adjacency matrix $A$, number of communities $K$.}
  \KwResult{Community assignments $1, ..., K$}
  Initialize the clustering by assigning to each vertex a unique community 
  label.\;
  For each vertex $v_i$, reassign the label to match one of its neighboring 
  vertices, and compute the change in modularity for each reassignment.\;
  Reassign $v_i$ to the community that results in the most positive change in 
  modularity, if possible. If modularity does not increase by changing the 
  label, skip the vertex.\;
  Group vertices with the same label and treat as one vertex.\;
  Repeat steps (3) and (4) until termination or the desired number of 
  communities is estimated.
\end{algorithm}

>>>>

For modularity maximization, \citet{307cbeb9b1be48299388437423d94bf1} used the 
Extreme Points (EP) algorithm \cite{le2016}, which is specific to the case 
$K = 2$. In our simulation studies, we used the EP algorithm for $K = 2$ and 
the Louvain algorithm \cite{Blondel_2008} for $K > 2$.

The EP algorithm is described by the following:

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Modularity maximization (EP algorithm)}
  \KwData{Adjacency matrix $A$, number of communities $K = 2$.}
  \KwResult{Community assignments $1, ..., K$.}
  Embed vertices of the graph described by $A$ into the subspace constructed 
  by a low rank approximation of $A$ (e.g., by the first few eigenvectors of 
  $A$).\;
  Project the hypercube $[-1, 1]^n$ to $U_A$.\;
\end{algorithm}

The Louvain algorithm is described by the following:

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Modularity maximization (Louvain method)}
  \KwData{Adjacency matrix $A$, number of communities $K$.}
  \KwResult{Community assignments $1, ..., K$.}
  Initialize the clustering by assigning to each vertex a unique community 
  label.\;
  For each vertex $v_i$, reassign the label to match one of its neighboring 
  vertices, and compute the change in modularity for each reassignment.\;
  Reassign $v_i$ to the community that results in the most positive change in 
  modularity, if possible. If modularity does not increase by changing the 
  label, skip the vertex.\;
  Group vertices with the same label and treat as one vertex.\;
  Repeat steps (3) and (4) until termination or the desired number of 
  communities is estimated.
\end{algorithm}
